The Private School Network

### 2024-02-21 index.qmd
copy-edit slides

Visits from universities to schools yields a two-mode social network

@@

- Increase nonresident enrollment in response to declines in state funding  [@RN3753]
- Nonresident students more affluent, less likely to be Black or Latinx [@RN3685]

@@

- Institutional financial aid to convert admits [@RN3762]
- Recruiting interventions at earlier stages of enrollment funnel
  - "Student list" purchases [@RN4985]
  - Off-campus recruiting visits [@RN4758; @RN4934]
    - Out-of state visits to public high schools focus on affluent public schools, avoid non-white communities

@@

- Public school students: 5% attend "top 100" public univ; 2% attend top 100 private univ (Author calculations from HSLS 2009)
- Private school: 11% `@` top 100 public; 17% `@` top 100 private
- Nonsectarian private: 11% `@` top 100 public; 40% `@` top 100 private

@@

- Public and private universities may be targeting similar sets of schools
  - Direct competition or vying to be second choice for rejected applicant

@@

- "Edge" or "network tie" = off-campus recruiting vist
- "Vertices” = schools $i$ (mode 1) and universities $j$ (mode 2)
text
- School-by-university matrix; cell $a_{i,j}$ shows number of visits school $i$ received from univ $j$

@@

- university $i$ and university $j$ share an edge if they visit at least one high school in common
- "Weight" of the edge is number of high schools visited by both $i$ and $j$

@@

### All recruiting visits, public research universities {.caption}

@@

### All recruiting visits, public research universities {.caption}

@@

>>>>

Visits from universities to schools yield a two-mode social network

@@

- Increased nonresident enrollment in response to declines in state funding  [@RN3753]
- Nonresident students are more affluent, less likely to be Black or Latinx [@RN3685]

@@

- Institutional financial aid to convert admits [@RN3762]
- Recruiting interventions at earlier stages of enrollment funnel
  - "Student list" purchases [@RN4985]
  - Off-campus recruiting visits [@RN4758; @RN4934]
    - Out-of-state visits to public high schools focus on affluent public schools, avoid non-white communities

@@

- **Public school students**: 5% attend "top 100" public univ; 2% attend top 100 private univ (Author calculations from HSLS 2009)
- **Private school**: 11% `@` top 100 public; 17% `@` top 100 private
- **Nonsectarian private**: 11% `@` top 100 public; 40% `@` top 100 private

@@

- Public and private universities may be targeting similar sets of schools
  - Direct competition or vying to be second choice for rejected applicants

@@

- "Edge" or "network tie" = off-campus recruiting visit
- "Vertices” = schools $i$ (mode 1) and universities $j$ (mode 2)
- School-by-university matrix; cell $a_{i,j}$ shows number of visits school $i$ received from univ $j$

@@

- university $j_1$ and university $j_2$ share an edge if they visit at least one high school in common
- "Weight" of the edge is number of high schools visited by both $j_1$ and $j_2$

@@

### All recruiting visits, public universities {.caption}

@@

### All recruiting visits, private universities {.caption}

@@

### One-mode network, private universities {.caption}
